{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-06-25 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, a lot more notes added

\section{Accelerated gradient descent and PPM}
    Recent works from Ahn \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    In his works, Ahn explored the interpretation of Nesterov acceleration via PPM. 
    They proposed the idea of ``similar triangle" for unifying all varieties of Nesterov accelerated gradient. 
    They used PPM to derive several variations of the Nesterov accelerated gradient algorithms. 
    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergence rate for the accelerated gradient.
    Their analysis results in relatively simple arguments that exhibits powerful extensions to several variants of the Nesterov accelerated gradient. 
    \par\noindent
    Interestingly, the Nesterov accelerated gradient applies to PPM too; Guler \cite{guler_new_1992} did it two decades ago. 
    He uses the idea of a Nesterov acceleration sequence faithfully. 
    One recent development of the accelerated PPM is an algorithmic framework named: ``Universal Catalyst acceleration", proposed by Lin et al \cite{lin_universal_2015}. 
    It is an application of Guler's work in the context of variance-reduction stochastic gradient algorithms for machine learning. 
    \par\noindent
    In this section, we
    \begin{enumerate}
        \item State Nesterov accelerated gradient and their varieties, and point to the literature discussing them. 
        \item Derive the Nesterov accelerated gradient. 
        \item Derive the popular step size choices along with the convergence rate. 
    \end{enumerate}
    Some content will differ from Ahn's works because we hope to generalize these ideas for our own use.

>>>>

\section{Accelerated gradient descent and PPM}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    Ahn explored the interpretation of Nesterov acceleration via PPM. 
    They proposed the idea of ``similar triangle" for unifying all varieties of Nesterov accelerated gradient. 
    They used PPM to derive several variations of the Nesterov accelerated gradient algorithms. 
    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergence rate for the accelerated gradient.
    Their analysis results in relatively simple arguments that exhibits powerful extensions to several variants of the Nesterov accelerated gradient. 
    \par\noindent
    Interestingly, the Nesterov accelerated gradient applies to PPM too; Guler \cite{guler_new_1992} did it two decades ago. 
    He uses the idea of a Nesterov acceleration sequence faithfully. 
    One recent development of the accelerated PPM is an algorithmic framework named: ``Universal Catalyst acceleration", proposed by Lin et al \cite{lin_universal_2015}. 
    It is an application of Guler's work in the context of variance-reduction stochastic gradient algorithms for machine learning. 
    \par\noindent
    In this section, we
    \begin{enumerate}
        \item State Nesterov accelerated gradient and their varieties, and point to the literature discussing them. 
        \item Derive the Nesterov accelerated gradient. 
        \item Derive the popular step size choices along with the convergence rate. 
    \end{enumerate}
    Some content will differ from Ahn's works because we hope to generalize these ideas for our own use.
